%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Friggeri Resume/CV
% XeLaTeX Template
% Version 1.0 (5/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Adrien Friggeri (adrien@friggeri.net)
% https://github.com/afriggeri/CV
%
% Some edits by:
% Erwin Rooijakkers (erwinrooijakkers@gmail.com)
% Changed to a more professional and clean look by changing font and some other parameters.
% Contents added to someone who works in a laser lab.
% Version 1 (1/8/13)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX and the bibliography, if used,
% needs to be compiled with biber rather than bibtex.
% Furthermore, please install the font packs Adobe Garamond Pro and GillSans
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{friggeri-cv} % Add 'print' as an option into the square bracket to remove colors from this template for printing

\addbibresource{bibliography.bib} % Specify the bibliography file to include publications

\usepackage{tikz}
\usepackage{marvosym}
\usepackage{wasysym}
\usepackage{graphicx}
\begin{document}

\header{\addfontfeature{LetterSpace=20.0}\fontsize{36}{36}\selectfont\scshape Erwin Rooijakkers}\\{\selectfont\scshape Software Engineer }\\
{\selectfont\scshape  } % Your name and current job title/field


%----------------------------------------------------------------------------------------
%	SIDEBAR SECTION
%----------------------------------------------------------------------------------------

\begin{aside} % In the aside, each new line forces a line break
\section{Contact}
Your Street 22
Your City, Postcal Code
Country
~
\Mobilefone ~06-123456789
\Letter ~\href{mailto:yours@domain.com}{yours\\@domain.com}
\Keyboard ~\href{https://www.github.com/erooijak}{github.com/erooijak}
~
\section{Date of birth}
December xx, xxxx
\section{Languages}
Netherlands~mother~tongue
English fluent
~
\section{Certificates}
MTA Networking
Fundamentals
MTA Security Fundamentals
MTA Windows Server
Administration
Fundamentals
MS Programming in HTML5 with JavaScript and CSS3
MS Programming in C\#
MS Developing ASP.NET MVC Web Applications
OCA Java SE 7 Programmer
~
\section{Interests}
\emph{Professional:} \\Programming\\ Monitoring \\Testing \\Application Lifecycle Management \\\emph{Personal:} \\Programming \\Soccer \\Fitness \\Meditation
\end{aside}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{Work experience}

\begin{entrylist}
%------------------------------------------------
\entry
{2014--Current}
{ING}
{Amsterdam, Netherlands}
{\emph{DEV Engineer}
\begin{itemize}
\item Within a DevOps team I work on a C\#.NET full-stack application for employees.
\item Focus on realizing Continuous Delivery with build-deploy-test in private cloud.
\item \emph{Used techniques and technologies:} Continuous Delivery, Scrum, Cloud,
\mbox{DevOps}, ASP.NET MVC and Web Forms, Test-Driven Development,
\mbox{Specification} by \mbox{Example}, Team Foundation Server, CodedUI, C\#, Ruby, Python, PowerShell (Desired State \mbox{Configuration}), Nolio, AngularJS, REST, Web.
\end{itemize}}
%------------------------------------------------
\entry
{2013--2014}
{Sogyo}
{De Bilt, Netherlands}
{\emph{Software Engineer}
\begin{itemize}
\item Development and maintenance of a lunch ordering application for employees.
\item Self-study and attending seminars on software engineering practices.
\item \emph{Used techniques and technologies:} Continuous Delivery, ASP.NET, ASP.NET MVC, Domain-Driven Design, Java, C\#, Web.
\end{itemize}}
%------------------------------------------------
\end{entrylist}


%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}

\begin{entrylist}
%------------------------------------------------
\entry
{2011--2013}
{MSc {\normalfont Transpersonal Psychology and Consciousness Studies}}
{\\University of Northampton, United Kingdom}
{\emph{Transpersonal psychology attempts to translate spiritual principles into contemporary \mbox{scientifically} grounded language.} 
\\ Thesis: Madness or Mysticism? A Quantitative Exploration of the Differentiation \mbox{Between} Psychosis and Spiritual Experience.}
%------------------------------------------------
\entry
{2007--2011}
{BSc {\normalfont Liberal Arts \& Sciences (Bèta-gamma) (Major: Physics and Astronomy, Minor: Philosophy)}}
{\\Universiteit van Amsterdam, Netherlands}
{\emph{Bèta-gamma combines elements of exact sciences, life sciences, social science, economy and philosophy. The core idea of the bachelor is that complex problems cannot be solved from one field of study. } \\
Thesis: Searching for Interstellar Gas Powered by the Jets of the X-Ray Binary V404 Cyg. }
%------------------------------------------------
\end{entrylist}


%----------------------------------------------------------------------------------------
%	AWARDS SECTION (of in ons geval extracurriculair)
%----------------------------------------------------------------------------------------

\section{Hobby projects}
\begin{entrylist}
%------------------------------------------------
\entry
{2015}
{Oogstplanner.nl}
{Amsterdam, Netherlands}
{A together with permaculture friends developed tool using an open source operating system (Linux); relational database management system (PostgreSQL); .NET runtime (Mono); inversion of control container (Autofac), and unit-testing framework (Moq).}
%------------------------------------------------
\entry
{2014--Current}
{Structure and Interpretation of Computer Programs}
{Cambridge, United States}
{I am working through this classic course which uses Lisp to explain fundamental \mbox{programming} concepts. This is one example of various self-study projects.}
%------------------------------------------------
\entry
{2013--2014}
{Chia Chia!}
{Amsterdam, Netherlands}
{Development and sales of a biological fruit drink with a webshop build in Ruby on Rails.}
%------------------------------------------------

\end{entrylist}
\end{document}
